---
title: "hp_rent"
author: "sachin kalra"
date: "20 December 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
Data has already been prepared for exploration after handling missing values.
but here we start with original data set.

#Jist of the data set
```{r}
list.files()
ds<-read.csv("house_price_train.csv",stringsAsFactors = F)
ds<-tbl_df(ds)
dim(ds)
ds
```

# Starting with Our Target Variable - SalePrice
```{r}
summary(ds$SalePrice)
library(ggplot2)
options(scipen=1)
ggplot(ds,mapping=aes(x=SalePrice))+
  geom_histogram(bins = 35,aes(fill= ..count..))+
  scale_fill_gradient("Count", low="green", high="red")


```

# As we can see data is skewed lets try with logarithmic transformation of Sale Price to normalize it.


```{r}
ggplot(ds,mapping=aes(x=log(SalePrice)))+
  geom_histogram(bins = 35,aes(fill= ..count..))+
  scale_fill_gradient("Count", low="green", high="red")
```

thus logarithmic transformation of SalePrice normalized it.

Lets explore relationship between SalePrice and Location/Neighborhood

```{r}
ggplot(ds ,mapping = aes(x= Neighborhood, y = SalePrice,color = Neighborhood ))+
   theme(axis.text.x=element_text(angle=30))+geom_point()+geom_boxplot()
```



Let's compare Neighborhoods by mean SalePrice

```{r}
library(dplyr)
msp<-group_by(ds,Neighborhood) %>%
  summarise(M_Sale_Price=mean(SalePrice))
print(msp)

ggplot(msp) + 
  geom_bar(aes(Neighborhood, M_Sale_Price, fill = Neighborhood),position = "dodge", stat = "summary", fun.y = "mean")+
  theme(axis.text.x = element_text(angle = 30))
  
  

```




Now, We already had a look at Mean sale prices of different neighbourhoods, lets go a level down and analyze it on the geographical map.
```{r}
#loading lon/lat gathered data
n_data<-read.csv("n_data_lon_lat.csv")
n_data<-read.csv("n_data_lon_lat.csv")
colnames(n_data)<-c("lon","lat","name")
n_data$mean_sp<-msp$M_Sale_Price
#spatial analysis in r data data()
cc<-c(lat = 42.034722, lon = -93.62 )
cc_map<-get_map(cc,zoom = 12,source = "stamen",maptype = "toner-background" )


ggmap(cc_map) +
  geom_point(aes(lon, lat, color = name), data = n_data)
colnames(n_data)<-c("lon","lat","name")

ggmap(cc_map, base_layer = ggplot(n_data, aes(lon, lat))) +
  geom_point(aes(color = mean_sp))



```


Exploring relationship between, Living Area and Sale Price.

```{r}
options(scipen=999)
ggplot(ds, aes(x=GrLivArea,y=SalePrice,color = Neighborhood))+
  geom_point()

```

as we can see two major outliers in Edwards Neighbour hood, lets explore them more.

```{r}
filter(ds,Neighborhood == "Edwards", GrLivArea > 4000) %>%
  select(Id,SalePrice,Neighborhood, YearBuilt,YrSold)


```

Let's Examine Edwards-Neighborhood a bit more and identify our outliers

```{r}

eds<-filter(ds,Neighborhood == "Edwards") %>%
  select(SalePrice,Neighborhood,GrLivArea)
print(eds)
ggplot(eds,aes(x=GrLivArea,y=SalePrice,color=Neighborhood))+
  geom_point()

```


